---
output: github_document
date: "`r Sys.Date()`"
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "vignettes/img/README-",
  out.width = "100%"
)
```

<img src="vignettes/img/logo_huh.svg" align="right" width="20%"/>

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![Codecov test coverage](https://codecov.io/gh/SigurdJanson/huh/branch/main/graph/badge.svg)](https://app.codecov.io/gh/SigurdJanson/huh?branch=main)
<!-- badges: end -->


Learning R can be hard. R objects can be ... how may we put it ... intricate? Not only is there is a large variety of objects. That is common for well established programming languages. The issue is rather that sometimes things may look similar but have subtle differences. All in all handling R objects can be quite difficult for a beginner. For newbies it can be quite confusing, even intimidating. I know it was for me.



# huh!?


## What It Does

The "huh?" package wants to describe objects to make it easier to understand what they are, what they contain and how to handle them. *My success measure: How many times do you open the manual?* If "huh!?" reduces the number of occasions you start browsing through pages of the manual or your favourite R textbook, in that case this package is a huge success.

It basically offers only two functions:

1. `huh()`
1. `how()`

... because "Huh!?" must be easy to learn. You do not need to learn many functions and arguments by heart. You simply ask `huh(myObject)` or `how(myObject)` in the console and get your result.


**huh**. `huh()` describes an object. It gives you the basic **type**, the **class**, any **attributes** including the number of dimensions, and on what **paradigm** the object is based on. The paradigm tells you whether the object is based on S3, S4, reference or R6 classes.


**Example**.

```{r huh1, eval=TRUE, include=TRUE}
library(huh)
# integer vector
huh(1:3)

# integer matrix
xy <- matrix(1:4, 2)
huh(xy)

# function (i.e. a closure to be exact)
huh(mean)
```

**how**. `how()` tells you how you can access the contents of an object, which subsetting techniques work, and what the resulting type would be. Also for several objects `how()` provides further information that is useful when you use the objects.

The output groups subsetting techniques by output type so that it is quite easy what the output of a subsetting operation looks like. A matrix returns an atomic vector when the subset is 1-dimensional unless you add the argument `drop=FALSE`. But since `drop=TRUE` is the default `how()` shows you this:

```r
#> vector 
#> y[c(...)], y[c(...), ...], y[[...]]
```

The first line is the output type. The second line shows ways to subset the matrix that will return this type. `...` means that you can only use a single number or string as index; `c(...)` allows using a vector of indices.


**Example**.

```{r how1, eval=TRUE, include=TRUE}
library(huh)
# atomic vector
x <- 1:3
how(x)

# 2-dimensional access
y <- matrix(1:4, 2)
how(y)

# function (...well, a closure to be exact)
how(mean) # not subsettable
```

That is all you need to know. 



## Installation

You can install the development version of huh from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("SigurdJanson/huh")
```


## Roadmap

The two big steps that are still missing.

* **Improved formatting** to enhance readability and bring attention to the essential details of the output.
* Enhanced **ease of use** of the output. It should be possible to just copy/paste output to use it.
* Finish an accompanying vignette about this package and types in R, in general.


Take a look at the [issues of the repository](https://github.com/SigurdJanson/huh/issues) if you want to know details.

If you find anything suspicious or you have an idea, just let me know. I am just a regular guy, not an R wizard and I am just trying to be a bit helpful, here. So don't hesitate if you notice something.



## Further Reading

Norberg, R. (2012). [Classes and Objects in R](https://www.r-bloggers.com/2012/10/classes-and-objects-in-r/). R Bloggers. *last access 2022-08-20*


