---
output: github_document
date: "`r Sys.Date()`"
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "vignettes/img/README-",
  out.width = "100%"
)
```

# huh

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

## What It Does

R objects can be ... "shady". There is a large variety of objects. Though they may look similar the difference can make their handling quite difficult. For newbies it can be quite confusing, even intimidating.

The "huh?" package wants to describe objects to make it easier to understand what they contain and how to handle them.



## Example


```{r huh1, eval=TRUE, include=TRUE}
library(huh)
huh(1:3)
xy <- matrix(1:4, 2)
huh(xy)
huh(mean)
```


## Installation

You can install the development version of huh from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("SigurdJanson/huh")
```



<!-- `huh` distinguishes different OOP paradigms with the field `paradigm`. -->

## Sources

http://adv-r.had.co.nz/OO-essentials.html
https://adv-r.hadley.nz/oo.html



